---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# neotomaTargets

`neotomaTargets` is a template for reproducible research using data from the [Neotoma database](https://www.neotomadb.org/) using the [`targets`](https://books.ropensci.org/targets/) pipeline.

It includes sample code for downloading data from Neotoma, cleaning the data, analysing the data, and writing a manuscript with R markdown, all in a `targets` pipeline.

# Installation

`neotomaTargets` is a [template repository](https://docs.github.com/en/github/creating-cloning-and-archiving-repositories/creating-a-repository-on-github/creating-a-repository-from-a-template). 

Click on the `#0000ff`Use this template`#0000ff` button  and follow the instructions to make a copy of this repo into your own account.

`neotomaTargets` depends on the `neotoma` and `targets` packages and some others listed in the DESCRIPTION file.
To install these packages, use

```{r, eval = FALSE}
devtools::install_deps()
```


# TODO

- [] targets plan to download, and clean neotoma data
- [] example analysis
- [] example manuscript with bibliography
