---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# neotomaTargets

`neotomaTargets` is a template for reproducible research using data from the [Neotoma database](https://www.neotomadb.org/) using the [`targets`](https://books.ropensci.org/targets/) pipeline.

It includes sample code for downloading data from Neotoma, cleaning the data, analysing the data, and writing a manuscript with R markdown, all in a `targets` pipeline.

The aim is that you can make a copy of the template and modify it to write your own reproducible manuscripts.

# Installation

`neotomaTargets` is a [template repository](https://docs.github.com/en/github/creating-cloning-and-archiving-repositories/creating-a-repository-on-github/creating-a-repository-from-a-template). 

Click on the :green_square: ` Use this template` :green_square:  button and follow the instructions to make a copy of this repo into your own account.

`neotomaTargets` depends on the `neotoma` and `targets` packages and some others listed in the DESCRIPTION file.
To install these packages, use

```{r, eval = FALSE}
devtools::install_deps()
```

# Using neotomaTemplate

To run all the analyses and produce the manuscript, open "make.R" and run `tar_make()`.
This finds the target plan in "_targets.R" (this file must have this name and be in the working directory), which is assembled from sub-plans in "R/*-plan.R" files.
If you modify any of the sub-plans and re-run `tar_make()` only targets which have been outdated will be re-run.
